---
title: Model Comparison Report
author: Generated by [hdnom.io](http://hdnom.io)
date: "`r Sys.Date()`"
graphics: yes
---

```{r, echo = FALSE}
opts_chunk$set(echo = FALSE, comment = NA, 
               fig.width = 8, fig.height = 8)
```

# Model Comparsion by Validation

## Validation Plot

Plot of the validation result:

```{r plot_compare_validate}
calcedCompareValidate = calcCompareValidate()
plot(calcedCompareValidate, interval = input$compare_validate_interval)
```

## Validation Summary

Model validation summary:

```{r summary_compare_validate}
summary(calcedCompareValidate)
```

## Validation Information

Basic information about model validation:

```{r print_compare_validate}
print(calcedCompareValidate)
```

# Model Comparison by Calibration

## Calibration Plot

Plot of the calibration result:

```{r plot_compare_calibrate}
calcedCompareCalibrate = calcCompareCalibrate()
plot(calcedCompareCalibrate,
     xlim = c(input$compare_calibrate_xlim_lo, input$compare_calibrate_xlim_up),
     ylim = c(input$compare_calibrate_xlim_lo, input$compare_calibrate_xlim_up))
```

## Calibration Summary

Model calibration summary:

```{r summary_compare_calibrate}
summary(calcedCompareCalibrate)
```

## Calibration Information

Basic information about model calibration:

```{r print_compare_calibrate}
print(calcedCompareCalibrate)
```

<hr>

Model comparison report generated at `r Sys.time()`.

Web app: [hdnom.io](http://hdnom.io) | Project home: [hdnom.org](http://hdnom.org)

# Session Information

```{r sessioninfo}
sessionInfo()
```
