---
title: Nomograms for High-Dimensional Cox Models
author: Generated by [hdnom.io](http://hdnom.io)
date: "`r Sys.Date()`"
graphics: yes
---

```{r, echo = FALSE}
opts_chunk$set(echo = FALSE, comment = NA, 
               fig.width = 8, fig.height = 8)
```

# Nomogram Plotting

## Nomogram

The plotted nomogram:

```{r plot_nomogram}
calcedNomogram = calcNomogram()
plot(calcedNomogram$'nom')
```

## Nomogram Summary

Basic information about the nomogram:

```{r print_nomogram}
print(calcedNomogram$'nom')
```

# Model Validation

## Validation Plot

Plot of the validation result:

```{r plot_validate}
calcedValidate = calcValidate()
plot(calcedValidate)
```

## Validation Summary

Model validation summary:

```{r summary_validate}
summary(calcedValidate)
```

## Validation Information

Basic information about the validation:

```{r print_validate}
print(calcedValidate)
```

# Model Calibration

## Calibration Plot

Plot of the calibration result:

```{r plot_calibrate}
calcedCalibrate = calcCalibrate()
plot(calcedCalibrate,
     xlim = c(input$calibrate_xlim_lo, input$calibrate_xlim_up),
     ylim = c(input$calibrate_xlim_lo, input$calibrate_xlim_up))
```

## Calibration Summary

Model calibration summary:

```{r summary_calibrate}
summary(calcedCalibrate)
```

## Calibration Information

Basic information about the calibration:

```{r print_calibrate}
print(calcedCalibrate)
```

<hr>

Report generated by hdnom web application at `r Sys.time()`.

Web app: [hdnom.io](http://hdnom.io) | Project home: [hdnom.org](http://hdnom.org)
